Data Analysis Project

### 2024-08-05 products/manuscript/Manuscript.qmd
commit changes

---
title: "Data Analysis Project"
subtitle: DA-6833
author: Rinu Thomas
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
csl: ../../assets/apa.csl
---

>>>>

---
title: "Data Analysis Project"
subtitle: DA-6833
author: Rinu Thomas
date: "`r Sys.Date()`"
format:
  docx:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../assets/dataanalysis-references.bib
---
